Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2016-01-25 CVPR16/rebuttal2.tex

\vspace{-0.4cm}
\paragraph{R24: Baselines}
For object-point association, the BBox baseline uses 3D bounding boxes with simple depth ordering. For suggested baseline with less weight closer to the boundary -- in a sense, our association probability is a principled way to compute such a weight. For localization, we note that [33] does not account for point tracks and as R24 notes, uses a database of highly detailed CAD models and discrete modeling, so is not directly comparable. We thank R24 for the suggested baseline that fits a 3D bounding box on the reconstructed point cloud (using SFM within detection bounding boxes), yielding \hili{XXX}\% error in t and \hili{XXX}\% in dim. We will add these in Table 2.
%the results are shown in Table \ref{tab:localization}. 
Here, we rely on size priors for unobservable dimensions in traffic scenes (say, when 3D points on only back of car are visible).

\vspace{-0.4cm}
\paragraph{R24: Typos in equations}
Thanks, $\cE_{\textrm{dyn}}$ and $\cE_{\textrm{size}}$ terms must be summed over all objects ($\cE_{\textrm{track}}$ in Eqn 15 already is), dependence on $\{ \Omega^i (t-1) \}_i$ in Eqn 19 must be dropped.

\vspace{-0.4cm}
\paragraph{R24: Number of objects} 
This is known a priori in our occlusion model (from object tracking [2]) and is also provided to other methods such as BBox and RAS.

%\vspace{-0.4cm}
%\paragraph{R24: Handling outliers} 
%As noted by R24, outliers are inherently handled in our model. Outlier tracks usually have high reprojection errors and thus, low association probabilities. Additionally, outlier detection bounding boxes are likely to be filtered out by object tracking.

%\vspace{-0.4cm}
%\paragraph{R24: Sequences for experiments} 
%We use all the sequences in the KITTI raw dataset (\hili{XXX} sequences, \hili{XXX} frames, \hili{XXX} object tracks).

\vspace{-0.4cm}
\paragraph{R24: Related works}
Thank you, we will cite them.

@@

\begin{table}[!!t]
\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
 & Symbol & Description \\
\hline
\hline
\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
 & $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
\hline
\hline
\multirow{5}{*}{\rotatebox{90}{Estimated}} & $\bp^c(t)$ & Position of camera at time $t$ \\
 & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
 & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
 & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
 & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ (independent of $t$) \\
\hline
\hline
\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of associating feature track $j$ with object $O_i$ \\	
 & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
 & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
 & $\bB^i$ & 3D dimensions of object $O_i$ (independent of time $t$) \\
\hline
\end{tabular}
\vspace{-0.2cm}
\caption{Notation of input and output.}
\label{tab:notations}
\vspace{-0.5cm}
\end{table}

\vspace{-0.4cm}
\paragraph{R26: Superiority over baselines}
Figure 5 may be considered with Table 1, which provides separate results for static and dynamic objects. Methods like BM and RAS cannot handle point tracks on static objects. BBox does start with both depth and motion information, but makes a hard assignment. In contrast, our formulation can incorporate point tracks, bounding boxes and detection scores in a unified probabilistic framework.

@@

\vspace{-0.4cm}
\paragraph{R26: Role of reflection and transmission probabilities}
Transmission probability only indicates whether a ray is transmissible to a particular depth, reflection probability indicates which object obstructs the ray at that depth. Thus, a combination of transmission and reflection probabilities is necessary to explain image observations. Lines 260-274 describe this intuition.

\vspace{-0.4cm}
\paragraph{R26: Increase in error with occlusion modeling}
We empirically choose parameters to minimize energy with both bounding box and point track occlusions. The same parameters are used for all experiments. Thus, error might be higher when modeling tracks or bounding boxes individually, but low when considered jointly. These parameters can be learned for a particular localization application, but our focus is more general -- to show that a continuous probabilistic occlusion model can be designed which is flexible enough to simultaneously handle point tracks and bounding boxes.

\vspace{-0.4cm}
\paragraph{R26: Parameters}
We use \hili{XXX}. The final version will include a detailed list of parameters.

### 2016-01-25 CVPR16/Source/occlusion.tex
changes

\begin{figure}
  \usetikzlibrary{calc}
  \centering
  \begin{tikzpicture}
    \input{Source/reflectiontransmissiongraph.tex}
  \end{tikzpicture}
  \vspace{-0.3cm}
  \caption{\small We represent traffic participants as soft ellipsoids which lead to formulation of transmision and reflection probability. This figure shows the reflection probability for the first car which is highest around the camera facing face of the car. Also note that transmission probability is inversly proportional to occupancy.}
  \label{fig:reflectiontransimission}
  \vspace{-0.3cm}
\end{figure}

>>>>

\begin{figure}
  \usetikzlibrary{calc}
  \centering
  \begin{tikzpicture}
    \input{Source/reflectiontransmissiongraph.tex}
  \end{tikzpicture}
  \vspace{-0.3cm}
  \caption{\small We represent objects as translucent ellipsoids which allows formulation of transmision and reflection probabilities. This figure shows the reflection probability for the first object (violet) which is highest closer to the camera. Also note that the transmission probability is inversely proportional to occupancy.}
  \label{fig:reflectiontransimission}
  \vspace{-0.3cm}
\end{figure}

### 2016-01-25 CVPR16/supplementarymaterial.tex
changes

\usepackage{verbatim}
\usepackage{bm}
\usepackage{microtype}
\usepackage{url}
\usepackage{multirow}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs} % for better tables

@@

\begin{document}
\title{A Continuous Occlusion Model for Road Scene Understanding}

@@

\section{Computation of Ellipsoids}
\label{sec:sigmacomputation}
Here we present how to compute the parameters of ellipsoids representing the occupancy of traffic participants. For an object $O_i$, let $\bB^i = [l~w~h]$ be its 3D dimensions, where $l$, $w$ and $h$ are respectively its length, width, and height on the ground plane, we are interested in calculating the center $\muic$ and spread $\Sigmaicf$ of the ellipsoid representing the occupancy of $O_i$ with respect to the camera coordinate system $\cC$ of the current frame.

Consider an object coordinate system $\cO$, which has the same orthonormal axes as the camera coordinate system and the origin at the projected point of the object center to the ground plane. For an object $O_i$, the center $\muit$ and spread $\Sigmait$ of the ellipsoid representing the occupancy of $O_i$ in the object coordinate system are expressed as
\begin{align}
  \muit &= \begin{bmatrix}
  0& 0& \frac{h}{2}
  \end{bmatrix}^\top,\\
  \Sigmait &= \begin{bmatrix}
    \frac{4}{l^2} & 0 & 0 \\
    0 & \frac{4}{w^2} & 0 \\
    0 & 0 & \frac{4}{h^2}
  \end{bmatrix}.
\end{align}

In object coordinates, the ellipsoid equation is written as
\begin{align}
  (\xt - \muit)^\top \Sigmait (\xt - \muit) = 1,
\label{equ:ellipsoidobj}
\end{align}
where $\xt$ is a point in object coordinates. Given $\Omega^i$ as the pose of $O_i$ in camera coordinates, we can extract the rotation $\Rctot$ and translation $\tctot$ for converting points in camera coordinates to object coordinates and rewrite \eqref{equ:ellipsoidobj} as
\begin{align}
  (\Rctot \xc + \tctot - \muit)^\top \Sigmait (\Rctot \xc + \tctot - \muit) = 1,
\label{equ:ellipsoidobj1}
\end{align}
where $\xc$ is a point in camera coordinates.

Let $\tcmut = \tctot - \muit$, \eqref{equ:ellipsoidobj1} becomes
%\begin{align}
%  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
%\end{align}
\begin{multline}
  \xc^\top \Rctot^\top \Sigmait \Rctot \xc + 2 (\Rctot^\top \tcmut)^\top  \Rctot^\top\Sigmait \Rctot \xc
  \\
  + \tcmut^\top \Sigmait \tcmut = 1.
\
\label{equ:ellipsoidobj2}
\end{multline}
Next, denote $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
\tcmut$, \eqref{equ:ellipsoidobj2} becomes
\begin{multline}
  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic 
  \\
  + \tcmut^\top \Sigmait \tcmut = 1.
\end{multline}
Finally, denote $\Sigmaicf = \frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
\muic^\top\Sigmaic\muic}$, we have the ellipsoid equation in camera coordinates
\begin{align}
(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1.
\label{equ:ellipsoidcam}
\end{align}

@@

\section{Other Energies for 3D Object Localization}
We present in this section the details of other energies, namely dynamic and size energies (in addition to point track and detection bounding box energies), that are used in our localization experiment.

@@

\subsection{Dynamic energy}
Dynamic energy imposes both temporal smoothness and holonomic constraints. In particular, holonomic constraints penalize changes in object position that are not in the direction of object orientation at the previous time step as
\begin{align}
  \label{eq:totalPosTransitionEnergy}
  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1}),
\end{align}
while temporal smoothness constraints add a penalty for unsmooth changes in object orientation and velocity over consecutive time steps as
\begin{align}
  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2,\\
  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2.
\end{align}
As a consequence, dynamic energy is expressed as a weighted combination of holonomic and smoothness constraints
\begin{align}
  \Energy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel},
\end{align}
where $\lambda_{\text{dyn-hol}}$, $\lambda_{\text{dyn-ori}}$ and $\lambda_{\text{dyn-vel}}$ are the weights of component energies.

\subsection{Size energy}
Size energy imposes prior knowledge on object dimensions as
\begin{align}
  \label{eq:totalSizeEnergy}
  \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
  \expDimsn),
\end{align}
where $\expDimsn$ and $\Sigma_{\expDimsn}$ are respectively the mean and covariance of object dimensions obtained from the KITTI dataset.

>>>>

\usepackage{verbatim}
\usepackage{bm}
\usepackage{microtype}
\usepackage{url}
\usepackage{multirow}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs} % for better tables
\usepackage{microtype}

@@

\begin{document}
\title{Supplement: A Continuous Occlusion Model for Road Scene Understanding}

@@

\section{Computation of Ellipsoids}
\label{sec:sigmacomputation}
In this section, we present computation of the parameters of ellipsoids representing occupancy of traffic participants. For an object $O_i$, let $\bB^i = [l~w~h]$ be its 3D dimensions, where $l$, $w$ and $h$ are its length, width and height on the ground plane, respectively. We wish to calculate the center $\muic$ and spread $\Sigmaicf$ of the ellipsoid representing the occupancy of $O_i$ with respect to the camera coordinate system $\cC$ of the current frame.

Consider an object coordinate system $\cO$, which has the same orthonormal axes as the camera coordinate system and the origin at the projected point of the object center on the ground plane. For an object $O_i$, the center $\muit$ and spread $\Sigmait$ of the ellipsoid representing the occupancy of $O_i$ in the object coordinate system are expressed as
\begin{align}
  \muit &= \begin{bmatrix}
  0& 0& \frac{h}{2}
  \end{bmatrix}^\top,\\
  \Sigmait &= \begin{bmatrix}
    \frac{4}{l^2} & 0 & 0 \\
    0 & \frac{4}{w^2} & 0 \\
    0 & 0 & \frac{4}{h^2}
  \end{bmatrix}.
\end{align}
In object coordinates, the ellipsoid equation is written as
\begin{align}
  (\xt - \muit)^\top \Sigmait (\xt - \muit) = 1,
\label{equ:ellipsoidobj}
\end{align}
where $\xt$ is a point in object coordinates. Given $\Omega^i$ as the pose of $O_i$ in camera coordinates, we can extract the rotation $\Rctot$ and translation $\tctot$ for converting points in camera coordinates to object coordinates and rewrite \eqref{equ:ellipsoidobj} as
\begin{align}
  (\Rctot \xc + \tctot - \muit)^\top \Sigmait (\Rctot \xc + \tctot - \muit) = 1,
\label{equ:ellipsoidobj1}
\end{align}
where $\xc$ is a point in camera coordinates.

Let $\tcmut = \tctot - \muit$, then \eqref{equ:ellipsoidobj1} becomes
%\begin{align}
%  (\Rctot \xc + \tcmut)^\top \Sigmait (\Rctot \xc + \tcmut) = 1
%\end{align}
\begin{multline}
  \xc^\top \Rctot^\top \Sigmait \Rctot \xc + 2 (\Rctot^\top \tcmut)^\top  \Rctot^\top\Sigmait \Rctot \xc
  \\
  + \tcmut^\top \Sigmait \tcmut = 1.
\
\label{equ:ellipsoidobj2}
\end{multline}
Next, denote $\Sigmaic = \Rctot^\top \Sigmait \Rctot$ and $\muic = - \Rctot^\top
\tcmut$, then \eqref{equ:ellipsoidobj2} becomes
\begin{multline}
  (\xc - \muic)^\top\Sigmaic(\xc - \muic) - \muic^\top\Sigmaic\muic 
  \\
  + \tcmut^\top \Sigmait \tcmut = 1.
\end{multline}
Finally, denoting $\Sigmaicf = \displaystyle\frac{\Sigmaic}{1 - \tcmut^\top \Sigmait \tcmut +
\muic^\top\Sigmaic\muic}$, we have the ellipsoid equation in camera coordinates
\begin{align}
(\xc - \muic)^\top\Sigmaicf(\xc - \muic) = 1.
\label{equ:ellipsoidcam}
\end{align}

@@

\section{Other Energies for 3D Object Localization}
This section provides the details of other energies, namely dynamic and size energies (in addition to point track and detection bounding box energies already presented in the main paper), that are used in our localization experiment.

@@

\subsection{Dynamic energy}
Dynamic energy imposes both temporal smoothness and holonomic constraints. In particular, holonomic constraints penalize changes in object position that are not in the direction of object orientation at the previous time step, as
\begin{align}
  \label{eq:totalPosTransitionEnergy}
  \Energy{dyn-hol} = 1 - \ori{i}{t-1} \cdot (\pos{i}{t} - \pos{i}{t-1}).
\end{align}
Temporal smoothness constraints add a penalty for unsmooth changes in object orientation and velocity over consecutive time steps, as
\begin{align}
  \Energy{dyn-ori} &= \|\ori{i}{t} - \ori{i}{t-1}\|^2,\\
  \Energy{dyn-vel} &= \|(\pos{i}{t} - 2\pos{i}{t-1}) + \pos{i}{t-2}\|^2.
\end{align}
The total dynamic energy is expressed as a weighted combination of holonomic and smoothness constraints
\begin{align}
  \Energy{dyn} &= \WEnergy{dyn-hol} + \WEnergy{dyn-ori} + \WEnergy{dyn-vel},
\end{align}
where $\lambda_{\text{dyn-hol}}$, $\lambda_{\text{dyn-ori}}$ and $\lambda_{\text{dyn-vel}}$ are the weights of the component energies.

\subsection{Size energy}
Size energy imposes prior knowledge on object dimensions as
\begin{align}
  \label{eq:totalSizeEnergy}
  \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
  \expDimsn),
\end{align}
where $\expDimsn$ and $\Sigma_{\expDimsn}$ are the mean and covariance, respectively, of object dimensions obtained from the KITTI dataset.
